### 2021-12-24 chapters/02-chapter-2.tex
txs auto checkin

\begin{small}
	\begin{longtable}{ | p{5cm} | p{2cm} | p{2cm} | p{2cm} | }
		\caption{Kontribusi \textit{critical path} dalam \textit{trace} \textit{baseline} dan regresi}
		\label{corr-tab-2}                                                           
		\\ \hline
		\centering\bfseries{\textit{Service} / Operasi} & \centering\bfseries{\textit{Baseline}} & \centering\bfseries{Regresi} & \centering\bfseries{Perubahan} \tabularnewline \hline
		\endfirsthead
		inventory/write-cache & 63.1 ms & 368 ms & +305 ms \\ \hline
		inventory-db/update & 1.75 ms & 2.26 ms & +0.51 ms \\ \hline
		memcached/set & 4.94 ms & 4.71 ms & -0.23 ms \\ \hline
		inventory/update-inventory & 63.1 ms & 368 ms & +305 ms \\ \hline

>>>>

\begin{small}
	\begin{longtable}{ | p{5cm} | p{2cm} | p{2cm} | p{2cm} | }
		\caption{Kontribusi \textit{critical path} dalam \textit{trace} \textit{baseline} dan regresi}
		\label{corr-tab-2}                                                           
		\\ \hline
		\centering\bfseries{\textit{Service} / Operasi} & \centering\bfseries{\textit{Baseline}} & \centering\bfseries{Regresi} & \centering\bfseries{Perubahan} \tabularnewline \hline
		\endfirsthead
		inventory/write-cache & 63.1 ms & 368 ms & +305 ms \\ \hline
		inventory-db/update & 1.75 ms & 2.26 ms & +0.51 ms \\ \hline
		memcached/set & 4.94 ms & 4.71 ms & -0.23 ms \\ \hline
		inventory/update-inventory & 15.2 ms & 14.8 ms & -0.47 ms \\ \hline
